### 2023-03-15 Conference Submission/DraftDoc.tex
Various edits to draft doc

\begin{section}{Conclusion}
    In this paper, we proposed a novel framework for modelling temporal networks. We then tested this framework on three types of small, synthetic network sequences. Throughout these tests the neural network performed ______, with the _____ sequence being especially notable due to ____. These results were likely because _____. In contrast, when we used symbolic regression to approximate the neural network model, we saw that _____.
\end{section}

>>>>

\begin{section}{Conclusion}
    In this paper, we proposed a novel framework for modelling temporal networks. We then tested this framework on three types of small, synthetic network sequences. Throughout these tests the neural network performed XXXXXXX, with the XXXXXX sequence being especially notable due to XXXXX. These results were likely because XXXXX. In contrast, when we used symbolic regression to approximate the neural network model, we saw that XXXXX.
\end{section}
